droptlet

### 2021-08-17 analysis/bayes_droplet.Rmd
kok

```{r eval= FALSE}
model10 <- brm(`dv10` ~ 1,
                  family = hurdle_gamma(link = "log", 
                                        link_shape = "log", 
                                        link_hu = "logit"),
                  data = droplet, save_pars = save_pars(all = TRUE))

model11 <- brm(`dv10` ~ solution,
                  family = hurdle_gamma(link = "log", 
                                        link_shape = "log", 
                                        link_hu = "logit"),
                  data = droplet, save_pars = save_pars(all = TRUE))

model12 <- brm(`dv10` ~ solution + nozzle,
                  family = hurdle_gamma(link = "log", 
                                        link_shape = "log", 
                                        link_hu = "logit"),
                  data = droplet, save_pars = save_pars(all = TRUE))

model13 <- brm(`dv10` ~ solution * nozzle,
                  family = hurdle_gamma(link = "log", 
                                        link_shape = "log", 
                                        link_hu = "logit"),
                  data = droplet, save_pars = save_pars(all = TRUE))
```

# dv50

@@

```{r}
library(bayestestR)
#bayesfactor_models(model11, model12, model13, denominator = model10)
# There are extreme evidence for model13 (interaction)
```

@@

```{r}
model21 <- brm(`dv50` ~ solution,
                  family = hurdle_gamma(link = "log", 
                                        link_shape = "log", 
                                        link_hu = "logit"),
               warmup = 1000, iter = 2000, chains = 4,
               prior = set_prior("student_t(0.5, 1, 2)", class = "b"),
                  data = droplet, save_pars = save_pars(all = TRUE))

model22 <- brm(`dv50` ~ solution + nozzle,
                  family = hurdle_gamma(link = "log", 
                                        link_shape = "log", 
                                        link_hu = "logit"),
               warmup = 1000, iter = 2000, chains = 4,
               prior = set_prior("student_t(0.5, 1, 2)", class = "b"),
                  data = droplet, save_pars = save_pars(all = TRUE))

model23 <- brm(`dv50` ~ solution * nozzle,
                  family = hurdle_gamma(link = "log", 
                                        link_shape = "log", 
                                        link_hu = "logit"),
               warmup = 1000, iter = 2000, chains = 4,
               prior = set_prior("student_t(0.5, 1, 2)", class = "b"),
                  data = droplet, save_pars = save_pars(all = TRUE))
```

```{r}
# model comparison
bayesfactor_models(model22, model23, denominator = model21)
```

@@

```{r}
emmeans4$emmeans %>% as_tibble() -> em4
emmeans5$emmeans %>% as_tibble() -> em5
```
```{r}
droplet %>% 
  unite("trt", c("solution", "nozzle"), sep = "-") %>% 
  dplyr::select(trt, rs) %>% 
  rename(response = rs) -> droplet2
```

>>>>

@@

```{r}
#library(bayestestR)
#bayesfactor_models(model11, model12, model13, denominator = model10)
# There are extreme evidence for model13 (interaction)
```

@@

```{r}
model23 <- brm(`dv50` ~ solution * nozzle,
                  family = hurdle_gamma(link = "log", 
                                        link_shape = "log", 
                                        link_hu = "logit"),
               warmup = 1000, iter = 2000, chains = 4,
               prior = set_prior("student_t(0.5, 1, 2)", class = "b"),
                  data = droplet, save_pars = save_pars(all = TRUE))
```

```{r}
# model comparison
#bayesfactor_models(model22, model23, denominator = model21)
```

@@

```{r}
emmeans4$emmeans %>% as_tibble() -> em4
emmeans5$emmeans %>% as_tibble() -> em5
```

```{r}
droplet %>% 
  unite("trt", c("solution", "nozzle"), sep = "-") %>% 
  dplyr::select(trt, rs) %>% 
  rename(response = rs) -> droplet2
```

### 2021-08-17 analysis/combined.Rmd
kok

```{r message = FALSE}
# Packages
options(scipen = 999)
library(rstanarm)
library(brms)
library(scales)
library(tidyverse)
library(emmeans)
library(ggthemes)
library(ggpmisc)
library(cowplot)
library(patchwork)
library(multcomp)
library(ggtext)
library(ggeffects)
library(agricolae)
library(extrafont)
library(showtext)
showtext_auto()
font_add_google("Playfair Display", ## name of Google font
                "Playfair")  ## name that will be used in R
font_add_google("Bangers", "Bangers")

>>>>

```{r message = FALSE}
# Packages
options(scipen = 999)
library(rstanarm)
library(brms)
library(scales)
library(tidyverse)
library(emmeans)
library(ggthemes)
library(ggpmisc)
library(cowplot)
library(patchwork)
library(multcomp)
library(ggtext)
library(ggeffects)
library(agricolae)
library(extrafont)
library(showtext)
showtext_auto()
font_add_google("Lato", ## name of Google font
                "lato")  ## name that will be used in R
font_add_google("Roboto", "roboto")

### 2021-08-17 analysis/droplet.Rmd
kok

```{r}
library(tidyverse)
library(glmmTMB)
library(emmeans)
library(betareg)
library(lme4)
library(multcomp)
library(lmerTest)
library(car)
library(brms)
```

@@

```{r}
readxl::read_excel("droplet_size_data.xlsx") %>% 
  janitor::clean_names() %>% 
  mutate_if(is_character, as_factor) %>% 
  group_by(solution, nozzle) %>% 
  mutate(nozzle = fct_recode(nozzle, 
                             "ULD12003" = "ULD11003")) %>% 
  mutate(x200 = x200/100) %>% 
  mutate(rep = row_number()) -> droplet
```

@@

```{r}
cld1 <- cld(emmeans1, alpha=0.05, Letters=letters, adjust="none", reversed = TRUE) %>% 
  as_tibble()
cld1
```

@@

```{r}
cld2 <- cld(emmeans2, alpha=0.05, Letters=letters, adjust="none", reversed = TRUE) %>% 
  as_tibble()
cld2
```

@@

```{r}
emmeans3 <- emmeans(model3, ~ nozzle * solution, type = "response")
```

```{r}
cld3 <- cld(emmeans3, alpha=0.05, Letters=letters, adjust="none", reversed = TRUE) %>% 
  as_tibble()
cld3
```

@@

```{r}
emmeans4 <- emmeans(model4, ~ nozzle * solution, type = "response")
```

```{r}
cld4 <- cld(emmeans4, alpha=0.05, Letters=letters, adjust="none", reversed = TRUE) %>% 
  as_tibble()
cld4
```

@@

```{r}
cld5 <- cld(emmeans5, alpha=0.05, Letters=letters, adjust="none", reversed = TRUE) %>% 
  as_tibble() 
cld5
```

>>>>

```{r}
library(tidyverse)
library(glmmTMB)
library(emmeans)
library(betareg)
library(lme4)
library(multcomp)
library(lmerTest)
library(car)
library(ggthemes)
library(ggrepel)
library(ggtext)
library(patchwork)
```

```{r}
library(extrafont)
library(showtext)
showtext_auto()
font_add_google("Lato", ## name of Google font
                "lato")  ## name that will be used in R
font_add_google("Roboto", "roboto")
```

@@

```{r}
readxl::read_excel("droplet_size_data.xlsx") %>% 
  janitor::clean_names() %>% 
  mutate_if(is_character, as_factor) %>% 
  group_by(solution, nozzle) %>% 
  mutate(nozzle = fct_recode(nozzle, 
                             "ULD12003" = "ULD11003")) %>% 
  mutate(x200 = x200/100) %>% 
  mutate(rep = row_number()) %>% 
  mutate(solution = str_replace_all(solution, "Intact", "DRA")) %>% 
  group_by(solution, nozzle) %>% 
  mutate(nozzle = str_remove_all(nozzle, '[0-9]+')) %>% 
  unite("trt", c(solution, nozzle), sep = "-", remove = FALSE) -> droplet
```

@@

```{r}
cld1 <- cld(emmeans1, alpha=0.05, Letters=letters, adjust="none", reversed = TRUE) %>% 
  as_tibble() %>% 
  mutate(type = "Dv10")
cld1
```

@@

```{r}
cld2 <- cld(emmeans2, alpha=0.05, Letters=letters, adjust="none", reversed = TRUE) %>% 
  as_tibble() %>% 
  mutate(type = "Dv50")

cld2
```

@@

```{r}
emmeans3 <- emmeans(model3, ~ nozzle * solution, cont="pairwise", type = "response")
```

```{r}
cld3 <- cld(emmeans3$emmeans, alpha=0.05, Letters=letters, 
            adjust="none", reversed = TRUE) %>% 
  as_tibble() %>% 
  mutate(type = "Dv90")
cld3
```

```{r}
cld1 %>% 
  bind_rows(cld2) %>% 
  bind_rows(cld3) %>% 
  group_by(solution, nozzle) %>% 
  mutate(nozzle = str_remove_all(nozzle, '[0-9]+')) %>% 
  unite("trt", c(solution, nozzle), sep = "-") %>% 
  mutate(response = round(response, 1)) -> dv
```

```{r}
library(scales)
show_col(brewer_pal(palette = "Set1")(5))
show_col(wsj_pal()(9))
```
```{r}
dv
droplet %>% 
  mutate(solution = str_replace_all(solution, "Intact", "DRA")) %>%
  pivot_longer(cols = c("dv10", "dv50", "dv90"), names_to = "type",
                             values_to = "dv") %>% 
  mutate(type = str_to_title(type)) -> droplet1
```

```{r}
dv %>% 
  ggplot(aes(x = fct_reorder(trt, response), 
             y = response, 
             color = trt, 
             shape = type)) +
  geom_point(size = 2, position = position_dodge2(width = 0.4)) +
  geom_linerange(aes(ymin = asymp.LCL, ymax = asymp.UCL),
                 position = position_dodge2(width = 0.4), 
                 size = 1.3) +
  geom_jitter(data = droplet1 %>% 
                rename(response = dv), 
                position = position_dodge2(width = 0.4),
              mapping = aes(color = trt, shape = type), alpha = 0.1, size = 2) +
  coord_flip() +
  geom_text_repel(aes(label = response, 
                         x = trt, color = trt, shape = type),
                    size = 8,
                    force_pull = 0,
                    direction = "y",
                    point.padding = NA,
                    min.segment.length = 14,
                    vjust = 0.5,
                    position = position_dodge2(width = 0.4),
                    seed = 455) +
#  annotate("text", x = 6, y = 300, label = "Dv10", size = 10,
#           color = "#E41A1C", fontface = "bold") +
#  annotate("text", x = 5.5, y = 800, label = "Dv50", size = 10,
#           color = "#377eb8", fontface = "bold") +
#  annotate("text", x = 4.5, y = 1250, label = "Dv90", size = 10, 
#           color = "#4daf4a", fontface = "bold") +
#  annotate("text", x = 1.2, y = 820, 
#           label = "There are differences \namong all pairwise trt \ncomparisons within \neach Dv (P <.0001)", size = 7.5, hjust = 0, lineheight = 0.3,
#           color = 1, fontface = "italic") +
  labs(x = NULL, y = "Droplet size (µm)", color = NULL, shape = NULL) +
  scale_color_viridis_d(option = "H") +
  scale_y_continuous(limits = c(0, 1500), breaks = seq(0, 1500, 300)) +
  scale_shape_manual(values = c(8,9,10)) +
  theme_few(base_family = "lato") + 
  theme(legend.position = c(0.8, 0.2),
        legend.text = element_markdown(size = 20),
        legend.background = element_blank(),
        axis.title = element_markdown(size = 30),
        axis.text = element_markdown(size = 25)) +
  guides(color = "none") -> fig1
```

@@

```{r}
emmeans4 <- emmeans(model4, ~ nozzle * solution, cont = "pairwise", type = "response")
```

```{r}
cld4 <- cld(emmeans4$emmeans, alpha=0.05, Letters=letters, adjust="none", reversed = TRUE) %>% 
  as_tibble() %>% 
  mutate(solution = str_replace_all(solution, "Intact", "DRA")) %>% 
  group_by(solution, nozzle) %>% 
  mutate(nozzle = str_remove_all(nozzle, '[0-9]+')) %>% 
  unite("trt", c(solution, nozzle), sep = "-") %>% 
  mutate(response = round(response, 2))
cld4
```

```{r}
cld4 %>% 
  ggplot(aes(x = fct_reorder(trt, response), y = response, color = trt)) +
  geom_point(size = 2, position = position_dodge2(width = 0.4)) +
  geom_linerange(aes(ymin = asymp.LCL, ymax = asymp.UCL),
                 position = position_dodge2(width = 0.4), size = 1.3) +
  coord_flip() +
  geom_jitter(data = droplet1 %>% 
                rename(response = rs), 
              mapping = aes(color = trt), alpha = 0.1, size = 2) +
  geom_text_repel(aes(label = response, 
                         x = trt),
                    size = 8,
                    force_pull = 0,
                    direction = "y",
                    point.padding = NA,
                    min.segment.length = 14,
                    vjust = 0.5,
                    position = position_dodge2(width = 0.4),
                    seed = 455) +
  annotate("text", x = 5, y = 0.1, label = "There are differences \namong all pairwise trt  \ncomparisons (P <.0001) \nin figures A, B and C", size = 9, hjust = 0, lineheight = 0.3,
           color = 1, fontface = "italic") +
  labs(x = NULL, y = "Relative spam", color = NULL) +
  scale_color_viridis_d(option = "H") +
  scale_y_continuous(limits = c(0, 1.2), breaks = seq(0, 1.2, 0.2)) +
  theme_few(base_family = "lato") + 
  theme(legend.position = "none",
        axis.title = element_markdown(size = 30),
        axis.text = element_markdown(size = 25)) -> fig2
```

@@

```{r}
cld5 <- cld(emmeans5, alpha=0.05, Letters=letters, adjust="none", reversed = TRUE) %>% 
  as_tibble() %>% 
  mutate(solution = str_replace_all(solution, "Intact", "DRA")) %>% 
  group_by(solution, nozzle) %>% 
  mutate(nozzle = str_remove_all(nozzle, '[0-9]+')) %>% 
  unite("trt", c(solution, nozzle), sep = "-") %>% 
  mutate(emmean = round(emmean,3))
cld5
```

```{r}
cld5 %>% 
  ggplot(aes(x = fct_reorder(trt, emmean*100), y = emmean*100, color = trt)) +
  geom_point(size = 2, position = position_dodge2(width = 0.4)) +
  geom_linerange(aes(ymin = asymp.LCL*100, ymax = asymp.UCL*100),
                 position = position_dodge2(width = 0.4), size = 1.3) +
  coord_flip() +
  geom_jitter(data = droplet1 %>% 
                rename(emmean = x200), 
              mapping = aes(color = trt), alpha = 0.1, size = 2) +
  geom_text_repel(aes(label = emmean*100, 
                         x = trt),
                    size = 8,
                    force_pull = 0,
                    direction = "y",
                    point.padding = NA,
                    min.segment.length = 14,
                    vjust = 0.5,
                    position = position_dodge2(width = 0.4),
                    seed = 455) +
#  annotate("text", x = 2, y = 3, label = "There are differences \namong all pairwise trt \ncomparisons (P <.0001)", size = 9, hjust = 0, lineheight = 0.3,
#           color = 1, fontface = "italic") +
  labs(x = NULL, y = "% drifable fines < 200 µm", color = NULL) +
  scale_color_viridis_d(option = "H") +
  scale_y_continuous(limits = c(0, 8), breaks = seq(0, 8, 2)) +
  theme_few(base_family = "lato") + 
  theme(legend.position = "none",
        axis.title = element_markdown(size = 30),
        axis.text = element_markdown(size = 25)) -> fig3
```

```{r}
fig1 + fig2 + fig3 +
  plot_annotation(tag_levels = 'A') & 
  theme(plot.tag = element_text(size = 25, hjust = 0, vjust = 0))

ggsave("Figure 4.png", width = 9, height = 3)
```
